\textbackslash documentclass\{beamer\}
\textbackslash usetheme\{JuanLesPins\}
\textbackslash usepackage\{graphicx\}

\textbackslash setbeamertemplate\{navigation symbols\}\{\}
\textbackslash setbeamersize\{text margin left = 10mm,text margin right
= 10mm\}

\textbackslash setlength\{\textbackslash parskip\}\{20pt\}

\textbackslash begin\{document\}

\textbackslash begin\{frame\}{[}t{]}\textbackslash Large\textbackslash centering\textbackslash vspace\{0.25cm\}\textbackslash textbf\{\{SHRI
VISHNU ENGINEERING COLLEGE FOR WOMEN\}\}\textbackslash\textbackslash{}

\textbackslash vspace\{0.25cm\}\textbackslash includegraphics{[}width=0.2\textbackslash textwidth{]}\{vishnu
logo.png\}\textbackslash\textbackslash{}

\textbackslash huge\textbackslash centering\textbackslash textbf\{\textbackslash fontfamily\{ptm\}\textbackslash selectfont
\{BIBLIOSEEK\}\} \textbackslash\textbackslash{}

\textbackslash normalsize\textbackslash vspace\{0.5 cm\}
\textbackslash begin\{tabular\}\{l @\{\textbackslash hspace\{1cm\}\} l
@\{\textbackslash hspace\{1cm\}\} l @\{\textbackslash hspace\{1cm\}\}\}
L.SANJANA \& 22B01A4257 \& FRONTEND \textbackslash\textbackslash{}
K.KAVYA SRI \& 22B01A4241 \& BACKEND \textbackslash\textbackslash{}
T.JYOTHSNA \& 22B01A4240 \& GIT OPERATOR \textbackslash\textbackslash{}
M.SAI ANVIKA \& 22B01A4259 \& LATEX DESIGNER
\textbackslash\textbackslash{} K.RAMYA SATYA SRI \& 23B05A4205 \&
DOCUMENTATION \textbackslash\textbackslash{}

\textbackslash end\{tabular\} \textbackslash end\{frame\}

\textbackslash begin\{frame\}\{ABSTRACT\} \textbackslash hspace\{1
cm\}Our project is a library management system developed using Python's
tkinter and PIL libraries. It functions as a web application where users
login to access various features. After authentication, users can search
for books by their title and author. If a book is found in the database,
users are redirected to a page displaying its details and location
within the library. Our system also includes a feedback mechanism,
allowing users to read and provide feedback on books they have read.
This feedback serves as recommendations for other users. By providing a
platform for users to search, read, and contribute feedback, our project
aims to enhance the library experience and promote community engagement.

\textbackslash end\{frame\}

\textbackslash begin\{frame\}\{DATA FLOW DIAGRAM\}
\textbackslash centering\textbackslash includegraphics{[}width=0.8\textbackslash textwidth{]}\{Screenshot
2024-03-03 123842.png\} \textbackslash end\{frame\}

\textbackslash begin\{frame\}\{UNIQUENESS\}
\textbackslash begin\{itemize\} \textbackslash item Users can share
experiences through ratings and comments. \textbackslash item Enhances
user engagement and provides valuable insights. \textbackslash item
Prioritizes both user experience and system security.
\textbackslash item Secure login ensures only authorized access,
fostering privacy and data protection. \textbackslash item Strikes a
balance between user-centric design, security, and advanced
functionalities. \textbackslash item Unique and comprehensive solution
for library management. \textbackslash end\{itemize\}
\textbackslash end\{frame\}

\textbackslash begin\{frame\}\{TECH STACK\}
\textbackslash begin\{itemize\} \textbackslash item Python 3.x
\textbackslash item Tkinter \textbackslash item PIL (Python Imaging
Library) \textbackslash item MySQL(database)

\textbackslash end\{itemize\}

\textbackslash end\{frame\}

\textbackslash begin\{frame\}\{OVERVIEW\}
\textbackslash large\textbackslash centering\textbackslash vspace\{0.5
cm\}\textbackslash textbf\{\{COVER
PAGE\}\}\textbackslash\textbackslash{} \textbackslash vspace\{0.5
cm\}\textbackslash centering\textbackslash includegraphics{[}width=1
\textbackslash textwidth{]}\{BB1.jpeg\}

\textbackslash end\{frame\}

\textbackslash begin\{frame\}
\textbackslash large\textbackslash centering\textbackslash vspace\{0.5
cm\}\textbackslash textbf\{\{LOGIN
PAGE\}\}\textbackslash\textbackslash{} \textbackslash vspace\{0.5 cm\}
\textbackslash centering\textbackslash includegraphics{[}width=1\textbackslash textwidth{]}\{BB2.jpeg\}
\textbackslash end\{frame\}

\textbackslash begin\{frame\}
\textbackslash large\textbackslash centering\textbackslash vspace\{0.5
cm\}\textbackslash textbf\{\{ENTRY
PAGE\}\}\textbackslash\textbackslash{} \textbackslash vspace\{0.5 cm\}
\textbackslash centering\textbackslash includegraphics{[}width=1\textbackslash textwidth{]}\{BB3.jpeg\}
\textbackslash end\{frame\}

\textbackslash begin\{frame\}
\textbackslash large\textbackslash centering\textbackslash vspace\{0.5
cm\}\textbackslash textbf\{\{DETAILS\}\}\textbackslash\textbackslash{}
\textbackslash vspace\{0.5 cm\}
\textbackslash centering\textbackslash includegraphics{[}width=1\textbackslash textwidth{]}\{BB4.jpeg\}
\textbackslash end\{frame\}

\textbackslash begin\{frame\}
\textbackslash large\textbackslash centering\textbackslash vspace\{0.5
cm\}\textbackslash textbf\{\{FEEDBACK\}\}\textbackslash\textbackslash{}
\textbackslash vspace\{0.5 cm\}
\textbackslash centering\textbackslash includegraphics{[}width=1\textbackslash textwidth{]}\{BB5.jpeg\}
\textbackslash end\{frame\}

\textbackslash begin\{frame\}\{BIBLIOGRAPHY\}
\textbackslash begin\{itemize\} \textbackslash item
https://readme.so/editor \textbackslash item
https://www.activestate.com/resources/quick-reads/how-to-position-widgets-in-tkinter/\#:\textasciitilde:text=Tkinter\%20has\%20three\%20built\%2Din,and\%20relative\%20to\%20each\%20other
\textbackslash item https://youtu.be/UjuPn6qyeYw?si=y6LfAVrN6Ju-pQJn
\textbackslash item https://youtu.be/Rtpu2cWz7W8?si=S0j3bt2m6K4B0CgM
\textbackslash item CHATGPT \textbackslash item BLACKBOX.AI

\textbackslash end\{itemize\}

\textbackslash end\{frame\}

\textbackslash end\{document\}
